Draft

### 2024-07-05 Bootstrap.Rmd
Cleaner document to sum up

```{r}
cat("Un intervalle de confiance à 95% par la méthode BCa est : [", res$confpoints[1,2], ";", res$confpoints[2,2], "]")
```

>>>>

```{r}
cat("Un intervalle de confiance à 95% par la méthode BCa est : [", res$confpoints[1,2], ";", res$confpoints[2,2], "]")

# Ex:
# Un intervalle de confiance à 95% par la méthode BCa est : [ 22154.37 ; 44308.74 ]
```

### 2024-07-05 Draft/Draft.Rmd
Cleaner document to sum up

>>>>

# Alarm / beep / message when it finishes running

```{r}
#Have R email you when it's done running.
###Calculating - your wish is R's command.
library(mail)
#Send yourself an email - specify your preferred email address, subject, and message. The password is fixed at "rmail".
sendmail("xxxxx@xxxxx.com", subject="Notification from R", message="Conditions finished running!", password="rmail")

alarm()

install.packages("audio")
library(audio)
install.packages("beepr")
library(beepr)
beep()
```
